Merging Datasets Through Deep learning

### 2018-09-03 paper2018/siamese_networks.tex
mess with figures
figures
minor changes

Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we used to build a system for merging data using Keras and Tensorflow.  As stated earlier, input is initially triples of a name, i.e., an \textit{anchor}, a \textit{positive} and a \textit{negative}.  During the tokenization process, we kept punctuation such as `-', `,', and `.' in the name because they are important signals in processing a name.  For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity.  A 100 dimensional character embedding was computed for each token in the entity using pretrained character embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.  We used character rather than word embeddings primarily because many names were missing from word based vector embeddings.

@@

\begin{figure*}[htb]
    \centering
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{schroff_triplet}
        \caption{Triplet loss}
        \label{schroff_loss}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{modified_loss}
        \caption{Modified loss}
        \label{modified_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{angular_loss}
        \caption{Angular loss}
        \label{angular_loss}
    \end{subfigure}
    \caption{Loss functions}
\end{figure*}

>>>>

Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we implemented to build the models using Keras and Tensorflow.  As stated earlier, input is initially triples of a name, i.e., an \textit{anchor}, a \textit{positive} and a \textit{negative}.  During the tokenization process, we kept punctuation such as `-', `,', and `.' in the name because they are important signals in processing a name.  For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity.  A 100 dimensional character embedding was computed for each token in the entity using pretrained character embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.  We used character rather than word embeddings primarily because many names were missing from word based vector embeddings.

@@

\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{schroff_triplet}
        \caption{Triplet loss}
        \label{schroff_loss}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.3\linewidth}
        \centering 
        \includegraphics[width=\linewidth]{modified_loss}
        \caption{Modified loss}
        \label{modified_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.3\linewidth}
        \centering 
        \includegraphics[width=\linewidth]{angular_loss}
        \caption{Angular loss}
        \label{angular_loss}
    \end{subfigure}
    \caption{Loss functions}
\end{figure}
